---
title: "TWIST-EFS – TLFs for ROP"
date: "August 7, 2025"
format:
  pdf:
    toc: true
    documentclass: article
    keep-md: true
    geometry: landscape
    mainfont: Calibri
    fontsize: 11pt
    pdf-engine: xelatex
    include-in-header: header.tex
---


```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
#install.packages("tinytex")
#tinytex::install_tinytex()

#quarto::quarto_install_tinytex()

library(knitr)
library(dplyr)
library(tibble)
library(flextable)
library(tinytex)
library(officer)
library(stringr)
library(lubridate)
library(ggplot2)
library(lubridate)
library(stringr)
library(showtext)
library(patchwork)

load("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS/data_archive/data_2025JUL28.RData")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/makedata/mk_adsl.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/makedata/mk_adsv.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/makedata/mk_adststat.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/makedata/mk_adecho.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/makedata/mk_adcec.R")

# get n for enrolled pop
n_enrolled <- nrow(subset(adsl, EnrolledFl == "Y"))

# get n for implanted pop
n_implanted <- nrow(subset(adsl, ImplantedFl == "Y"))
```
{{< pagebreak >}}

# Table 2 Patient Disposition & Follow-up Visit Compliance by Interval

Enrolled Population (N=`r n_enrolled`)

```{r table2, message=FALSE, warning=FALSE}
#| echo: false
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t2_patientdisposition.R")

t2_patientdisposition
```
{{< pagebreak >}}

# Table 3 Demographics and Baseline Characteristics

Enrolled Population (N=`r n_enrolled`)

```{r table3, message=FALSE, warning=FALSE}
#| echo: false
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t3_baselinedem.R")
  
t3_baselinedem
```
{{< pagebreak >}}

# Table 4 Device Success at Exit from Or/Cath Lab (Per Device Analysis)

Enrolled Population (N=`r n_enrolled`)

```{r table4, message=FALSE, warning=FALSE}
#| echo: false
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t4_devicesuccess.R")
  
t4_devicesuccess
```
{{< pagebreak >}}

# Table 8: CEC Adjudicated Endpoints for Events up to 1 Year

Enrolled Population (N=`r n_enrolled`)

```{r table8, message=FALSE, warning=FALSE}
#| echo: false
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t8_CEC_MAEs.R")

t8_CEC_MAEs
```
{{< pagebreak >}}

# Table 11 CEC Adjudicated Heart Failure Hospitalizations and Non-elective Mitral Valve Reinterventions

Enrolled Population (N=`r n_enrolled`)

```{r table11, message=FALSE, warning=FALSE}
#| echo: false
#source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_2025_11_DSMB/programs/makedata/mk_adsl.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t11_CEC_HFH_MVR.R")

t11_CEC_HFH_MVR
```
{{< pagebreak >}}

# Table 13 NYHA Class: Unpaired Analysis

Implanted Population (N=`r n_implanted`)

```{r table13, message=FALSE, warning=FALSE}
#| echo: false
#source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_2025_11_DSMB/programs/makedata/mk_adsl.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t13_NYHA.R")

t13_NYHA
```
{{< pagebreak >}}

# Table 14 MR Grade by Core Lab TTE: Unpaired Analysis

Implanted Population (N=`r n_implanted`)

```{r table14, message=FALSE, warning=FALSE}
#| echo: false
#source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_2025_11_DSMB/programs/makedata/mk_adsl.R")
source("C:/Users/luke_hall/OneDrive - Edwards Lifesciences/lhall/TWIST_EFS_DSMB_2025NOV/programs/TLFs/t14_MRgrade.R")

t14_MRgrade
```
